\newglossaryentry{MSDN}
{
  name={MSDN},
  description={The Microsoft Developer Network is a central place for \emph{Windows} application programmers. It contains detailed information about the \emph{Windows} environment and documentation about the exported \emph{Windows} API functions},
  first={Microsoft Developer Network (MSDN)},
  long={Microsoft Developer Network}
}
\newglossaryentry{PMT}
{
  name={PMT},
  description={Process Memory Tampering describes the process of unwanted memory modifications of another process},
  first={Process Memory Tampering (PMT)},
  long={Process Memory Tampering}
}
\newglossaryentry{DLL}
{
  name={DLL},
  description={A Dynamic-link Library is a shared file that exports functions. This allows reuse of code and smaller application updates. Most DLLs are shipped by the operating system},
  first={Dynamic-link Library (DLL)},
  long={Dynamic-link Library}
}
\newglossaryentry{OS}
{
  name={OS},
  description={The operating system is a software that abstracts the computer's hardware and exports basic functionality for higher level applications},
  first={Operating System (OS)},
  long={Operating System}
}
\newglossaryentry{EULA}
{
  name={EULA},
  description={The End User License Agreement is a contract between a company and a user. It is widely used in software deployment to make a legal contract},
  first={End User License Agreement (EULA)},
  long={End User License Agreement}
}
\newglossaryentry{ESEA}
{
  name={ESEA},
  description={The eSports Entertainment Association is a Counterstrike league. Access costs a monthly subscription fee. Raised money is used for events and anti cheat development},
  first={eSports Entertainment Association (ESEA)},
  long={eSports Entertainment Association}
}
\newglossaryentry{API}
{
  name={API},
  description={An Application Programming Interface allows interaction with one software to another software},
  first={Application Programming Interface (API)},
  long={Application programming interface}
}
\newglossaryentry{WPM}
{
  name={WPM},
  description={\syscall{WriteProcessMemory} is an exported function of the \emph{Windows} API. This function allows memory modification of another process. A process handle with \syscall{PROCESS\_VM\_WRITE} permissions is required to use this function},
  first={\syscall{WriteProcessMemory} (WPM)},
  long={\syscall{WriteProcessMemory}}
}
\newglossaryentry{ASLR}
{
  name={ASLR},
  description={Address Space Layout Randomization is a defense against buffer overflow exploits which is described in Section~\ref{sec:aslr}},
  first={Address Space Layout Randomization (ASLR)},
  long={Address Space Layout Randomization}
}
\newglossaryentry{DEP}
{
  name={DEP},
  description={Data Execution Prevention is a security feature to prevent buffer overflow exploits. It is described in Section~\ref{sec:dep}},
  first={Data Execution Prevention (DEP)},
  long={Data Execution Prevention}
}
\newglossaryentry{MIC}
{
  name={MIC},
  description={Mandatory Integrity Control is a security model found in \emph{Windows} systems. It is described in Section~\ref{sec:mic}},
  first={Mandatory Integrity Control (MIC)},
  long={Mandatory Integrity Control}
}
\newglossaryentry{ACL}
{
  name={ACL},
  description={An Access Control List contains multiple Access Control Entries. It is used to determine if an object has the privilege to access another object},
  first={Access Control List (ACL)},
  long={Access Control List}
}
\newglossaryentry{ACE}
{
  name={ACE},
  description={An Access Control Entry is part of an ACL. It defines the granted or denied permissions of an object onto this object},
  first={Access Control Entry (ACE)},
  long={Access Control Entry}
}
\newglossaryentry{PID}
{
  name={PID},
  description={A Process ID uniquely identifies a process},
  first={Process ID (PID)},
  long={Process ID}
}
\newglossaryentry{IRQL}
{
  name={IRQL},
  description={The Interrupt Request Level is used inside \emph{Windows Kernel} programming. Interrupts can be signaled by different hardware components like a hard disk drive. If the IRQL is raised high enough, such Interrupts will not occur for the currently executed code},
  first={Interrupt Request Level (IRQL)},
  long={Interrupt Request Level}
}
\newglossaryentry{APC}
{
  name={APC},
  description={An Asynchronous Procedure Call is a function that is executed asynchronously in the context of another thread. Inside the kernel, it is used to deliver signals for important events (e.g., the end of a file read operation). Disabling APCs can lead to a deadlock},
  first={Asynchronous Procedure Calls (APC)},
  long={Asynchronous Procedure Call}
}