\newglossaryentry{msdn}
{
  name={MSDN},
  description={The Microsoft Developer Network is a central place for windows application programmers. It contains detailed information about the Windows environment and documentation about the exported Windows API functions.},
  first={Microsoft Developer Network (MSDN)},
  long={Microsoft Developer Network}
}
\newglossaryentry{PMT}
{
  name={PMT},
  description={Process Memory Tampering describes the process of unwanted memory modifications of another process.},
  first={Process Memory Tampering (PMT)},
  long={Process Memory Tampering}
}
\newglossaryentry{DLL}
{
  name={DLL},
  description={A Dynamic-link Library is a shared file that exports functions. This allows reuse of code and smaller application updates. Most DLLs are shipped by the operating system.},
  first={Dynamic-link Library (DLL)},
  long={Dynamic-link Library}
}
\newglossaryentry{OS}
{
  name={OS},
  description={The operating system is a software that abstracts the computer's hardware and exports basic functionality for higher level applications.},
  first={Operating System (OS)},
  long={Operating System}
}
\newglossaryentry{EULA}
{
  name={EULA},
  description={The End User License Agreement is a contract between a company and a user. It is widely used in software to make a legal contract.},
  first={End User License Agreement (EULA)},
  long={End User License Agreement}
}
\newglossaryentry{ESEA}
{
  name={ESEA},
  description={The eSports Entertainment Association is a Counterstrike league. Access costs a monthly subscription fee. Raised money is used for events and anti cheat development.},
  first={eSports Entertainment Association (ESEA)},
  long={eSports Entertainment Association}
}
\newglossaryentry{API}
{
  name={API},
  description={An Application programming interface allows interaction with one software to another software.},
  first={Application programming interface (API)},
  long={Application programming interface}
}
\newglossaryentry{WPM}
{
  name={WPM},
  description={\syscall{WriteProcessMemory} is an exported function of the Windows API. This function allows memory modification of another process. A process handle with \syscall{PROCESS\_VM_WRITE} permissions is required to use this function.},
  first={\syscall{WriteProcessMemory} (WPM)},
  long={\syscall{WriteProcessMemory}}
}
\newglossaryentry{ASLR}
{
  name={ASLR},
  description={Address Space Layout Randomization is a defense against buffer overflow exploits which is described in Section \ref{sec:aslr}},
  first={Address Space Layout Randomization (ASLR)},
  long={Address Space Layout Randomization}
}
\newglossaryentry{DEP}
{
  name={DEP},
  description={Data Execution Prevention is a security feature to prevent buffer overflow exploits. It is described in Section \ref{sec:dep}},
  first={Data Execution Prevention (DEP)},
  long={Data Execution Prevention}
}
\newglossaryentry{MIC}
{
  name={MIC},
  description={Mandatory Integrity Control is a security model found on Windows systems. It is described in Section \ref{sec:mic}},
  first={Mandatory Integrity Control (MIC)},
  long={Mandatory Integrity Control}
}
\newglossaryentry{ACL}
{
  name={ACL},
  description={An Access Control List contains multiple Access Control Entries. It is used to determine if an object has the privilege to access another object.},
  first={Access Control List (ACL)},
  long={Access Control List}
}
\newglossaryentry{ACE}
{
  name={ACE},
  description={},
  first={Access Control Entry (ACE)},
  long={Access Control Entry}
}
\newglossaryentry{PID}
{
  name={PID},
  description={A Process ID uniquely identifies a process.},
  first={Process ID (PID)},
  long={Process ID}
}
\newglossaryentry{IRQL}
{
  name={IRQL},
  description={The Interrupt Request Level is used inside Windows Kernel programming. Interrupts can be signaled by different hardware components like a hard disk drive. If the IRQL is raised high enough, such Interrupts will not occur for the currently executed code.},
  first={Interrupt Request Level (IRQL)},
  long={Interrupt Request Level}
}
\newglossaryentry{APC}
{
  name={APC},
  description={An asynchronous procedure call is a function that is executed asynchronously in the context of another thread. Inside the Kernel, it is used to deliver signals for important events like the end of a file read operation. Disabling APCs can lead to a deadlock.},
  first={Asynchronous Procedure Call (APC)},
  long={Asynchronous Procedure Call}
}