\subsubsection{\emph{Chrome} Defenses}
\paragraph{\emph{Chrome} ELF}
\emph{Google Chrome} contains a \syscall{chrome\_elf.dll} file that exports important and security relevant functions. The main two purposes are caching of function addresses and a \gls{DLL} blacklist. Chrome ELF is the first loaded module in Chrome and can be used to add more security features like setting a process security descriptor\footnote{This concept is evaluated later in chapter \ref{sec:dacl}}. However, as Google's development team states, they are not interested in protecting Chrome from user-mode attacks \cite{chromium_security}. This is due to the reason, that a malicious process running under privilege level as Chrome can gain access and modify Chrome's memory and settings. Instead, the user should rely on his installed anti-virus software to detect and prevent attacks.

\paragraph{Cached function addresses}
The second part of Chrome ELFs features is caching of function addresses of \syscall{ntdll.dll}. All exported functions are stored inside a function lookup table to increase speed and reduce lookup operations of these often used functions. Additionally, the virtual memory space of the function lookup table is set to \syscall{PAGE\_READONLY}, to ensure that this memory can no longer be modified. This adds no security, because an attacker (external or internal) will remove the set \syscall{PAGE\_READONLY} flag and modify the lookup table. Additionally, this feature creates a new threat that can be used for attacks. Entries of the lookup table are changed to new addresses, making the described \gls{API} hooking attacks of Section \ref{sec:attacks} even easier.

\paragraph{DLL Blacklist}
Chrome ELF contains a \gls{DLL} blacklist feature, which prevents unwanted \glspl{DLL} from being loaded into Chrome. The blacklist is split into two parts, the first contained inside the code and a second list loaded from the local computers registry. The existing detection algorithms checks for an existing entry in the blacklist by comparing the file- and imagename of the loaded \gls{DLL} file. If a blacklisted \gls{DLL} is found, it is unloaded from Chrome. A comparison between file-/imagenames is  weak, because an attacker can change the name of the \gls{DLL} file. Additionally, every new build of the blacklisted \gls{DLL} will not be detected if the name is changed. The whole purpose of the existing blacklist feature is to increase stability of Google Chrome and prevent unstable extensions and addons from running, to ensure an as optimal as possible user experience.