\subsection{Performance}
\label{sec:performance}
This section evaluates the performance of the driver and shows the impact on the \emph{Google Chrome} browser. At first, the impact on \emph{Chrome} is measured. Then, the time needed for hashing a \gls{DLL} file is measured.

\subsubsection{Hardware}
The performance measurement was done in a \emph{VirtualBox}\footnote{\url{https://www.virtualbox.org/}} virtual machine running \emph{Windows 7 64 bit}. Table~\ref{fig:hardware_host} shows the hardware used for the host computer. Table~\ref{fig:hardware_vm} shows the hardware assigned to the virtual machine. The virtual machine was stored on a RAID 1 setup with 50 GB of assigned storage. 
\begin{table}[bh]
\centering
\caption{Hardware of the host system}
\label{fig:hardware_host}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
Component & Used Hardware \\ \hline
CPU & Intel i7-2600k @ 3.5 GHz, 4 cores, 8 threads \\ \hline
RAM & 4 * 4 GB @ 1600 MHz \\ \hline
MAINBOARD & Asus P8Z68 deluxe/gen3 \\ \hline
SSD 1 & Mushkin Chronos 120 GB, 500 MB/s \\ \hline
SSD 2 & San Disk Pro 480 GB, 500 MB/s \\ \hline
RAID 1 & 2x Western Digital Caviar Green 2.5 TB, 170 MB/s \\ \hline
\end{tabularx}
\end{table}
\begin{table}[bh]
\centering
\caption{Assigned hardware of the virtual machine}
\label{fig:hardware_vm}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
Component & Used Hardware \\ \hline
CPU & Intel i7-2600k @ 3.5 GHz, 1 core, 2 threads \\ \hline
RAM & 4 GB @ 1600 MHz \\ \hline
\end{tabularx}
\end{table}

\subsubsection{General setup}
The experiments used \emph{Google Chrome} version \emph{48.0.2564.97 m} and disabled several services of the \emph{Windows} operating system to get more accurate test results. \emph{Windows Defender}, \emph{Windows Search} and \emph{Windows Update} were disabled for both, host and guest machine. Every test was executed ten times for each possible configuration. The information was acquired with \emph{Chrome's} internal profiler as discussed in Section~\ref{sec:profiler}. The measured data is described in Table~\ref{fig:ex1_duplicate}.
\begin{table}[hb]
\caption{This is a duplicate of Table~\ref{fig:ex1_info} of Section~\ref{sec:profiler} for the convenience of the reader}
\label{fig:ex1_duplicate}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
Information & Meaning \\ \hline
Count & The number of tasks that were executed \\ \hline
Queue time & The time between task creation and its execution in milliseconds \\ \hline
Run time & The time required to execute the task in milliseconds \\ \hline
Total & The sum of all values \\ \hline
Maximum & The maximum of all values \\ \hline
Average & The quotient of total and count \\ \hline
\end{tabularx}
\end{table}

\input{sections/evaluation/performance/experiment1.tex}
\clearpage
\input{sections/evaluation/performance/experiment2.tex}