In games, especially in online games that are based on a large amount of user-inputs, \gls{PMT} can be applied to create powerful cheats that are hard to detect. The cheater hereby has to reverse engineer the game once to receive a table of offsets. This table of offsets contains the relative memory locations, the relative addresses, that can be used to access important game information. In cheat forums, such a table is typicially represented in text format with key-value pairs \cite{offsets}. By directly changing the data of the game, \emph{aimbots}, \emph{wallhacks} and \emph{scripts} can be created easily. The unfair advantage gained by the cheat destroys the games audiences fun and in the long term significantly reduces the number of active players. Nevertheless cheats are used knowing these consequences, as the short term fun is more pleasant for the cheater. \gls{PMT} detection is a crucially important thing in online games like First Person Shooters, as the whole game play relies on user input, but often is very hard to achieve to due lack of knowledge and legal issues. Legal issues exist during the deployment of the users software, because an anti cheat application usually requires root access to detect cheats. However, this stands in contrast to data protection laws, which deny such deep access without the users permissions. The game developers then need to make a legal contract with the user, often defined within the \gls{EULA} or Terms of Service. Root access raises another problem, as the users might not trust the anti cheat developers because of pasts incidents. One example in the First Person Shooter area is the game \emph{Counterstrike: Global Offensive}, which is, according to the active players and viewers, the third most played e-Sports game. As such, several leagues exist which often ship their own anti cheat system. The \gls{ESEA}, a counterstrike league, was fined one million us-dollar by the US Superior Court of California, County of San Francisco \cite{esea} in case \emph{CGC-13-532593}, for secretly mining bitcoins in their anti cheat. 